---
title: "Get prices with Tdata"
author: "Alexis Martin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Prices may come from different sources, they can be real-time or not.
Real-time comes only from IBKR account.
The `price_vignette` provides prices from all different sources:

- In the past or real-time
- For one ticker or a set of tickers
- For one date or an interval date

## Functions list

## List of Documented Functions

This vignette provides a list of all documented functions in the package. Each function is linked to its corresponding help page.

```{r list-functions, echo=FALSE, results='asis'}
# List all .Rd files in the man directory
man_dir <- here::here("man")
rd_files <- list.files(man_dir, pattern = "\\.Rd$", full.names = TRUE)

# Extract function names (assuming the .Rd files correspond to function names)
function_names <- gsub(".*/(.*)\\.Rd", "\\1", rd_files)

# Generate HTML links to each .Rd file using the help() system
links <- sapply(function_names, function(fn) {
  href <- paste0("?", fn)  # Create link to the help page for each function
  paste0("<a href='", href, "'>", fn, "</a>")
})

# Output the list of functions as HTML
cat("<ul>")
for (link in links) {
  cat("<li>", link, "</li>")
}
cat("</ul>")
```
## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
